Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-09-29 manuscript/supplement_motifs.tex
minor changes

\section{Statistical analysis}
 \subsection*{How does species persistence vary with motif participation?}

            We are interested in whether participating more often in a certain motif (e.g., direct competition) might increase persistence.
            % (see \emph{Appendix SXX} for relationships between persistence and counts of motifs).
            To test this, we fit four linear mixed-effect models (LMMs; one per motif included in the Bayesian networks).
            These models included the proportion of the species' role made up by the focal motif, the level of disturbance to basal species, and the interaction between the two.
            We centered and scaled the predictors before fitting the LMMs.
            The models also included a random intercept for the interaction between species richness and connectance (equations.
            All models were fit using the R~\citep{R} function `lmer' from the package \emph{lmerTest}~\citep{lmerTest}.
            We calculated marginal (fixed effects only) and conditional (fixed and random effects) $R^2$ using the R~\citep{R} function `r.squaredGLMM' from the package \emph{MuMIn}~\citep{MuMIn}.

@@

            \begin{equation}
                \Psi_{ik} \approx \rho_{i} + \pi_{disturbed_k} + \rho_{i}\pi_{disturbed_k} +
                S:C_{i} ,
                \label{propreq}
            \end{equation}

@@

        \subsection*{How does motif participation vary with species and network properties?}

            As with network profiles, species' motif participation may covary with other measures of network structure and species' roles within the network.
            To establish this context for motif participation, we fit a linear mixed-effect model relating the frequency of participation in each motif to network size, connectance, and their interaction, as for network motif profiles (\emph{Appendix SG}).
            We also fit linear mixed-effect models relating the count or proportion of each motif to degree or trophic level and a random effect of the interaction between network size and connectance using the R~\citep{R} function `lmer' from the package \emph{lmerTest}~\citep{lmerTest}.
            We performed similar analyses to test whether a species' motif role is related it in-degree or trophic level (\emph{Appendix SI}).

        \subsection*{How does network mean persistence vary with motif profiles?}

@@

        \subsection*{How do network motif profiles vary with global structure?}

@@

        \subsection*{How does network mean persistence vary depending on network properties?}

@@

        \subsection*{How does persistence vary with degree and trophic level?}

>>>>

\section{Statistical analysis}

    \subsection{How does species persistence vary with motif participation?}

        We are first interested in whether participating more often in a certain motif (e.g., direct competition) might increase a species' probability of persistence.
        To test this, we fit four linear mixed-effect models (LMMs; one per motif included in the Bayesian networks):

        \begin{equation}
            \Psi_{ik} \approx \rho_{i} + \pi_{disturbed_k} + \rho_{i}\pi_{disturbed_k} +
            S_{i}:C_{i} ,
            \label{propreq}
        \end{equation}

        These models included the proportion of the species' role made up by the focal motif, the level of disturbance to basal species, and the interaction between the two.
        We centered and scaled the predictors before fitting the LMMs.
        The models also included a random intercept for the interaction between species richness and connectance (equations.
        All models were fit using the R~\citep{R} function `lmer' from the package \emph{lmerTest}~\citep{lmerTest}.
        We calculated marginal (fixed effects only) and conditional (fixed and random effects) $R^2$ using the R~\citep{R} function `r.squaredGLMM' from the package \emph{MuMIn}~\citep{MuMIn}.

@@

@@

    \subsection{How does motif participation vary with species and network properties?}

        As with network profiles, species' motif participation may covary with other measures of network structure and species' roles within the network.
        To establish this context for motif participation, we fit a linear mixed-effect model relating the frequency of participation in each motif to network size, connectance, and their interaction, as for network motif profiles (\emph{Appendix SG}).
        We also fit linear mixed-effect models relating the count or proportion of each motif to degree or trophic level and a random effect of the interaction between network size and connectance using the R~\citep{R} function `lmer' from the package \emph{lmerTest}~\citep{lmerTest}.
        We performed similar analyses to test whether a species' motif role is related it in-degree or trophic lev,el (\emph{Appendix SI}).

    \subsection{How does network mean persistence vary with motif profiles?}

@@

    \subsection{How do network motif profiles vary with global structure?}

@@

    \subsection{How does persistence vary with species and network properties?}

        \subsubsection{How does network mean persistence vary depending on network properties?}

@@

        \subsubsection{How does persistence vary with degree and trophic level?}
